---
output: pdf_document
papersize: letter
fontfamily: Verdana
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, cache = FALSE, dev = "cairo_pdf")

library(knitr) #for rendering the PDF
library(dplyr) # data munging
library(ggplot2) # fortify()
library(envreportutils) # theme_soe()
library(stringr) # for label wrapping
library(RColorBrewer) #for colour palette

read_chunk("04_output.R")

## Load clean data if not already in local repository
if (!exists("ta_type")) load("tmp/trans_gwlic_summaries.RData")
```


```{r pre}
```
<!--\pagenumbering{gobble}-->


# B.C. Groundwater Licensing Transition Project

\vspace{12pt}

# STATUS DASHBOARD: `r proctime_date`

\vspace{32pt}

```{r estimate, fig.height = 2, fig.width = 7}

```

\vspace{32pt}

```{r stage_rates, fig.height = 4, fig.width = 7}

```

\vspace{24pt}

Dashboard plot data sourced from (i) 'vFCBC Application Search' accessed on `r app_date` and (ii) FLNRO FCBC 'ATS system application processing time report' accessed on `r proctime_date`.

\newpage

# B.C. Groundwater Licensing Transition Project

\vspace{12pt}

# STATUS SUMMARIES

\vspace{32pt}

## FrontCounter BC: Applications Recieved, Processing & Acceptance 

Data sourced from 'vFCBC Application Search' and accessed on `r app_date`, projected estimates from ENV Water Protection & Sustainability Branch

\vspace{12pt}
  
```{r types, fig.height = 2, fig.width = 7}

```

\vspace{24pt}

```{r app_rate, fig.height = 4, fig.width = 7}

```


```{r app_regions, fig.height = 5, fig.width = 7}

```

\newpage

## FLNRO E-Licensing: Applications Under Adjudication 

Data sourced from FLNRO's E-licensing Home 'Incoming Groundwater Licence Application Tracking Report' and accessed on `r lic_date`

\vspace{12pt}

```{r incoming, fig.height = 2, fig.width = 7}

```

\vspace{14pt}

```{r water_use, fig.height = 6, fig.width = 7}

```

\newpage

## FLNRO E-Licensing: Transition Licence Status & Processing Time

Data sourced from FLNRO FCBC 'ATS system application processing time report' and accessed on `r proctime_date`

\vspace{24pt}

```{r line_facet, fig.height = 8, fig.width = 7}

```


